---
title: "Practical Machine Learning"
author: "kimsungguen"
date: "2015년 11월 20일"
output: 
  html_document: 
    keep_md: yes
---

## package import
```{r}
library(caret)
```


## path setting & data loading
```{r}
setwd("D:/git/github/plm1/PLM_submission")
testing_sub = read.csv("pml-testing.csv", head = TRUE)
pjdata = read.csv("pml-training.csv", head = TRUE)
```


## variable exploration 
  - number of variable : 160 variable
  - mode of variable : num, chr, Factor(three kind of variable)
  - kind of NA : NA,"","#DIV/0!" - three type of NA
```{r}
names(pjdata)
str(pjdata)
```


## data loading again for "NA" value preprocess  
  - Convert (NA,"","#DIV/0!") to  NA using  "na.strings" argument
```{r}
testing_sub = read.csv("pml-testing.csv", 
                       head = TRUE, 
                       na.strings = c(NA,"","#DIV/0!"))

pjdata = read.csv("pml-training.csv",
                  head = TRUE, 
                  na.strings = c(NA,"","#DIV/0!"))
```


## data cleaning
  - count NA each variables    
  - loading variables without NA columns to pjdata
```{r}
colSums(is.na(pjdata))
pjdata = pjdata[,colSums(is.na(pjdata)) == 0]
testing_sub = testing_sub[,colSums(is.na(testing_sub)) == 0]
names(pjdata)
```


  - deleted meaningless variables (columns 1~7)
```{r}
pjdata = pjdata[,-c(1:7)]
testing_sub = testing_sub[,-c(1:7)]
names(pjdata)
```


## data splitting
  - 70% of data for training, 30% of data for testing
```{r}
intrain = createDataPartition(y=pjdata$classe, p=0.7, list=FALSE)
training = pjdata[intrain,]
testing = pjdata[-intrain,]
dim(training) ; dim(testing)
```


## model fitting 
  - Used three models - 1)rpart, 2)random forest, 3)LDA
```{r}
tree_modfit = train(classe~., data=training , method="rpart")
tree_modfit
rf_modfit = train(classe~., data=training , method="rf")
rf_modfit
lda_modfit = train(classe~., data=training , method="lda")
lda_modfit
```


## prediction
  - prediction on testing data
```{r}
tree_test = predict(tree_modfit, testing)
rf_test = predict(rf_modfit, testing)
lda_test = predict(lda_modfit, testing)
```


## make confusion-matrix
   - rpart model's accuracy is about 50~77%
   - LDA models's accuracy is about 78~86%
   - random-forest model's accuracy is about 99%
```{r}
confusion_tree = confusionMatrix(tree_test, testing$classe)
confusion_tree
confusion_rf = confusionMatrix(rf_test, testing$classe)
confusion_rf 
confusion_lda = confusionMatrix(lda_test, testing$classe)
confusion_lda
```


## Results
  - It shows that random-forest model is better than other models
  
  
## submission (20 test sample)
```{r}
answers = predict(rf_modfit, testing_sub)

pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

pml_write_files(answers)
```  
  
  
  
  
  
  
  
  
  
  